---
output:
  html_document:
    keep_md: yes
---
## wbData

Excerpt of the World Bank indicator data on life expectancy, GDP per capita, population, land area, urban population(% of total), population aged 65 and above(% total), fertility rate by country, every year from 1960 to 2012.

### Description
* Source: [World Bank Data](http://data.worldbank.org/)
* 12 variables
- `country`: country name, factoer with 214 levels
- `country.code`: iso-2 code for each country, character
- `isoAlpha`: isoAlpha3 code for each country, character
- `continent`: continent name, factor with 6 levels
- `year`: ranges from 1960 to 2012
- `land.area`: land area, in square kilometers
- `life.exp`: life expectancy at birth, in years
- `fertility.rate`: the number of children that would be born to a woman
- `population`: total population
- `urban.pop`: percentage of urban population of total population
- `above65.pop`: percentage of population aged 65 or above of total population
- `gdp.per.capita`: GDP per capita in US dollars

### Install and test drive

Install `wbData` from Github:

```{r eval = FALSE}
devtools::install_github("JiyingWen/wbData")
```

Load it and test drive with some data aggregation and plotting:

```{r}
library(wbData)
aggregate(fertility.rate ~ continent, wbData, median)

suppressPackageStartupMessages(library(dplyr))
wbData %>%
    filter(year == 2012) %>%
    group_by(continent) %>%
    summarise(urban.pop = median(urban.pop))

library(ggplot2)
ggplot(subset(wbData, country == "Canada"), aes(x = year, y = urban.pop, color = country)) +
	geom_point(na.rm = TRUE) + geom_line()
  
```

